---
title: "Game Market"
author: "Chen Jing"
date: "12/12/2017"
output: ioslides_presentation
---
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
require(reshape2)
library(treemap)
library(tidyr)
library(wordcloud2)
library(stringr)
library(RColorBrewer)
library(tidytext)
library(tidyverse)
library(janeaustenr)
library(scales)
library(ggmap)
library(xlsx)
```

```{r,warning=FALSE, message=FALSE, echo=FALSE}
setwd('/Users/JingC/Desktop/MA 615/Final project/Game Market/')

Game <- read.csv('Video_Games_Sales_as_at_22_Dec_2016.csv')

NintendoData <- read.csv('NintendoData.csv', stringsAsFactors=FALSE)

Game$Year_of_Release<-as.numeric(as.character(Game$Year_of_Release))
```



##Introduction 
A video game is an electronic game that involves interaction with a user interface to generate visual feedback on a video device such as a TV screen or computer monitor. Recently, Newzoo released the latest quarterly update of its Global Games Market Report. It shows that 2.2 billion gamers across the globe are expected to generate $108.9 billion in game revenues in 2017. In this report, we will review the video game market through datasets provides by Metacritic.com and live topic-related text data from Twitter.com. 

##top 8 global sales game
```{r echo = FALSE}
top.10<-subset(Game[c(1:10),],select=c(Name,Platform,Genre,Publisher,Global_Sales))
knitr::kable(top.10)
```


##Video Game Publisher
Through 1980 to 2016, the top 10 publishers for overall sales video game are list in the following table. 

```{r,warning=FALSE, message=FALSE, echo=FALSE}
GamePublisher<-Game %>% group_by(Publisher) %>% 
summarise(Total.Sales = sum(Global_Sales),Avg.Sales=mean(Global_Sales)) %>% arrange(desc(Total.Sales)) %>%
top_n(n = 10, wt = Total.Sales)
kable(GamePublisher)
```


##Video Game Genre
Video game genres are used to categorize video games based on their gameplay interaction rather than visual or narrative differences.Unlike individual game, each game genre has some game developer. 
```{r,fig.align="center",warning=FALSE, message=FALSE, echo=FALSE,fig.height=3,fig.width=5}
treemap(Game,
index="Genre",
vSize="Global_Sales",
type="index",
title="Overall Video Games Sales for Various Genre ", #Customize your title
fontsize.title = 14 #Change the font size of the title
)


```


##Video Game Platform 
The electronic systems used to play video games are known as platforms. With the development of the game design, the graphic, sound, control technologies are changing in a short period in order to provides the best game service to the customers. 

```{r,warning=FALSE, message=FALSE, echo=FALSE,fig.height=3,fig.width=8}
PYear<-Game[-c(which(Game$Year_of_Release=='2017'),which(Game$Year_of_Release=='2020'),which(Game$Year_of_Release=='N/A'),which(Game$Genre=='')),]
PlatYear<-PYear[c(which(PYear$Platform=='PS2'),which(PYear$Platform=='X360'),which(PYear$Platform=='PS3'),which(PYear$Platform=='Wii'),which(PYear$Platform=='DS'),which(PYear$Platform=='PS')),]

platform.year <-ggplot(PYear, aes(Year_of_Release, Global_Sales))+geom_bar(stat = "identity", aes(fill = Platform))+ggtitle('Platform sales change over time')+ theme(plot.title = element_text(size = 20, face = "bold")) 
platform.year
```


##Nintendo Evaluation
Among the above popular game platform, DS and Wii are produced by game company Nintendo. However, as we could see from the plot, the overall sales for the two platform keep decreseaing since 2007. Does this indicate that Nintendo beign to lose in the game market? 

##Word Cloud

```{r, warning=FALSE, message=FALSE, echo=FALSE}
Nintendo<-NintendoData[c(which(NintendoData$tweets=='nintendo')),]
Nintendotweet<-as.vector(data.frame(Nintendo[[3]]))
Nintendotweet <- sapply(Nintendotweet, function(row) iconv(row, "latin1", "ASCII", sub=""))
Nintendo_text <- paste(Nintendotweet,collapse = "")

# Clean text
clean_tweet = gsub("&amp", "", Nintendo_text)
clean_tweet = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", clean_tweet)
clean_tweet = gsub("@\\w+", "", clean_tweet)
clean_tweet = gsub("[[:punct:]]", "", clean_tweet)
clean_tweet = gsub("[[:digit:]]", "", clean_tweet)
clean_tweet = gsub("http\\w+", "", clean_tweet)
clean_tweet = gsub("[ \t]{2,}", "", clean_tweet)
clean_tweet = gsub("^\\s+|\\s+$", "", clean_tweet) 
clean_tweet <- str_replace_all(clean_tweet," "," ")#get rid of unnecessary spaces
#clean_tweet <- str_replace_all(clean_tweet, "http://t.co/[a-z,A-Z,0-9]*{8}","") # Get rid of URLs
clean_tweet <- str_replace(clean_tweet,"RT @[a-z,A-Z]*: ","") # Take out retweet header
clean_tweet <- str_replace_all(clean_tweet,"#[a-z,A-Z]*","") # Get rid of hashtags
clean_tweet <- str_replace_all(clean_tweet,"@[a-z,A-Z]*","")# Get rid of references to other screennames 


Nintendo_df <- data_frame(text = clean_tweet)

Nintendo_df<-Nintendo_df %>% unnest_tokens(word, text)


Nintendo.tweet<-Nintendo_df %>%
anti_join(stop_words) %>%
count(word, sort=TRUE) 

wordcloud2(data = Nintendo.tweet)
```

##Cloud Text
From the word cloud we could see that postive word such as happy, birthday are mentioned a lot in the tweet text. The former company CEO Satoru Iwata was also appeared pretty frequent. It seems Nintendo brought many postive attitude with customers. 

##Sentiment Analysis
In order to evaluate customers' tweet attitude, sten sentiment test is applied in the following. Postive word such as thank, super, and happy are used quite often in tweets. And most of the negative words for example wild, crushing, and smash are usually part of the video game material. In general, people from twitter have a strong postive attituide related to Nintendo.

```{r, warning=FALSE, message=FALSE, echo=FALSE,fig.height=3,fig.width=6}
Nintendo<-NintendoData[c(which(NintendoData$tweets=='nintendo')),]
Nintendotweet<-as.vector(data.frame(Nintendo[[3]]))
Nintendotweet <- sapply(Nintendotweet, function(row) iconv(row, "latin1", "ASCII", sub=""))
Nintendo_text <- paste(Nintendotweet,collapse = "")
clean_tweet = gsub("&amp", "", Nintendo_text)
clean_tweet = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", clean_tweet)
clean_tweet = gsub("@\\w+", "", clean_tweet)
clean_tweet = gsub("[[:punct:]]", "", clean_tweet)
clean_tweet = gsub("[[:digit:]]", "", clean_tweet)
clean_tweet = gsub("http\\w+", "", clean_tweet)
clean_tweet = gsub("[ \t]{2,}", "", clean_tweet)
clean_tweet = gsub("^\\s+|\\s+$", "", clean_tweet) 
clean_tweet <- str_replace_all(clean_tweet," "," ")#get rid of unnecessary spaces
#clean_tweet <- str_replace_all(clean_tweet, "http://t.co/[a-z,A-Z,0-9]*{8}","") # Get rid of URLs
clean_tweet <- str_replace(clean_tweet,"RT @[a-z,A-Z]*: ","") # Take out retweet header
clean_tweet <- str_replace_all(clean_tweet,"#[a-z,A-Z]*","") # Get rid of hashtags
clean_tweet <- str_replace_all(clean_tweet,"@[a-z,A-Z]*","")# Get rid of references to other screennames 


Nintendo_df <- data_frame(text = clean_tweet)

Nintendo_df<-Nintendo_df %>% unnest_tokens(word, text)


Nintendo.tweet<-Nintendo_df %>%
anti_join(stop_words) %>%
count(word, sort=TRUE) 


janeaustensentiment <- Nintendo_df  %>%
inner_join(get_sentiments("bing")) 


bing_word_counts <-  Nintendo_df %>%
inner_join(get_sentiments("bing")) %>%
count(word, sentiment, sort = TRUE) %>%
ungroup()


bing_word_counts %>%
group_by(sentiment) %>%
top_n(10) %>%
ungroup() %>%
mutate(word = reorder(word, n)) %>%
ggplot(aes(word, n, fill = sentiment)) +
geom_col(show.legend = FALSE) +
facet_wrap(~sentiment, scales = "free_y") +
labs(y = "Contribution to sentiment",
x = NULL) +
coord_flip()

```

##R Shiny
For user interact plot, please visit the rshiny page
http://127.0.0.1:7533/
